\TheTitle

### 2016-04-22 linvis.tex
Editing Related Work and Methodologies

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around the tree-based model
instead of a DAG. Our tool provides information about the location of a given commit
in the respective merge tree, the files edited, the modules edited, and the commit
message for a given commit or merge. The tool allows users to apply various filters,
including the release version, along with a keyword or phrase from the log preview,
the name of the author, or the commit id. The user can request all the root-level
merges containing a commit or merge that matches the query, or all commits and
merges that match the query.

@@

To our knowledge, we know of no git repository visualization systems that builds a
tree from the merge. This may be because more information is required to generate
the trees than what is stored by git. Git uses a DAG model, which enables
history-altering actions like rebases to occur, whereas older tools like CVS and svn
construct trees\cite{CVS2008} but do not work with history-altering actions.

A server must sit and monitor the git repository as it changes over time to handle
changes to history. Many of the visualization tools are designed for a
general-purpose approach, where any repository is directly usable without additional
information. Polling for this additional information makes the application specific
to a repository or project.

@@

Gitk, Gitg, and other similar git repository visualizing tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. This suggests that Gitk and similar tools are designed for users
working from a given commit or leaf-node toward the root. With this model, it is
difficult for users to see what other commits are involved with a given merge.

Furthermore, the DAG model is only able to provide file-level information on a
commit level. It is unable to quickly aggregate the file data over all commits that
are part of a merge. If a user would like to view what files were edited at a merge,
they must manually aggregate this information by hand. While some merges are
relatively small, containing less than 10 commits, other merges are large,
containing over 1500 edited files, as in the case of commit \textit{73287a4}. This
issue is important for authorship and licensing. A merge can only show one author,
the contributor making the merge, but does not show who wrote the commits contained
within that merge.

@@

University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for
displaying the file structure of a given version of the kernel. Treemaps are good
for visualizing the topology of shallow, wide trees, making it a good candidate for
showing file systems. Treemaps are limited in what information can be displayed. The
information within the treemap does not provide clear insight on what changes were
made to the files in the given release, only providing information on where the file
is located within the file system. File systems and the merge tree of the kernel
share many similarities, in both cases, they represent trees that are wide and
shallow, suggesting that a treemap could potentially work to visualize the commit
and merge structure of the kernel.

@@

The treemap design is also designed for working with data of differing types.
In the filesystem, there are many kinds of files. There are text files,
scripts, images, binary files, and other types. These can be given colours
making differences stand out. There is no obvious way to assign meaningful
types to the commits such that all the commits within a given merge do not all
have the same colour.

@@

The goal is to build a tool that makes navigation of the kernel commit
information simpler, while providing an explanation of the changes occurring at
each commit and merge. We designed the tool with two use-cases in mind, though a
sumer may switch between the cases as they work.

\textit{Use-case 1: top-to-bottom approach}\label{sec:usecase1}\\
These are users that are maintaining a section of the kernel and would like to pick
a merge and merge it directly into their current repository, which is useful for
reducing the amount of re-implementation work. For them, it is
important to have the ability to aggregate files and modules that are being changed
somewhere in the merge. It is also important for them to be able to navigate from
the root toward the largest merge that contains only the commits that modify the
modules that they are working with.

\textit{Use-case 2: bottom-to-top approach}\label{sec:usecase2}\\
These are users that start with a known merge or commit and would like to see
what other changes are being made in commits that are in the same merge. This is
useful to see how changes in a given file will break other changes made in the
surrounding commits in the same merge. This is primarily for maintainers that need
to perform some implementation work in order to correctly merge patches from the
future. We must provide these users a mechanism for navigating from a single commit
toward the root, allowing them to see a bigger picture.

@@

We root the tree with the merge made by Linus. Each merge may contain zero or more
children, which are other merges and commits. If a merge is cherry-picked or rebased
there will be no children. Commits have no children and are always leaf nodes. The
commits contains the metadata for the changes made. This metadata includes the files
changed, the lines added and removed from each file, the author, the date the commit
was merged into the merge that led to being merged into the kernel, and the date the
commit was authored, the diff, and the commit log. Merges contain less metadata,
only storing the author of the merge, the log, the commit date, and the author date.
The details of the model are outlined by German \cite{German2015}.

>>>>

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around the tree-based model
instead of the DAG. Our tool provides information about the location of a given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. The tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit id. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

To our knowledge, we know of no git repository visualization systems that build
trees from the DAG provided by git. This may be because more information is required
to generate the trees than what is stored by git. Git uses a DAG model, which
enables history-altering actions, like rebases to occur, whereas older tools like
CVS and svn construct trees\cite{CVS2008} but do not work with history-altering
actions.

A server must sit and monitor the git repository as it changes over time to handle
the changes to history. Many of the visualization tools are designed for a
general-purpose approach, where any repository is directly usable without additional
information. Polling for this additional information makes the visualizer specific
to a repository or project.

@@

Gitk, Gitg, and other similar git repository visualization tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. This suggests that Gitk and similar tools are designed for users
working from a given commit or leaf-node toward the root. With this model, it is
difficult for users to see what other commits are involved with a given merge.

Furthermore, the DAG model is only able to provide file-level information for
commits. It is unable to quickly aggregate the file data over all commits that
are part of a merge. If a user would like to view what files were edited at a merge,
they must manually aggregate this information by hand. While some merges are
relatively small, containing less than 10 commits, other merges are large,
containing over 1500 edited files, as in the case of commit \textit{73287a4}. This
issue is important for authorship and licensing. A merge can only show one author,
the contributor making the merge, but does not show who wrote the commits contained
within that merge.

@@

University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for displaying the file structure of a given
version of the kernel. Treemaps are good for visualizing the topology of shallow,
wide trees, making it a good candidate for displaying file systems. Treemaps are
limited in what information can be displayed. The information within the treemap
does not provide clear insight on what changes were made to the files in the given
release, only providing information on where the file is located within the file
system, that is they do no provide temporal information. File systems and the merge
tree of the kernel share many similarities, in both cases, they represent trees that
are wide and shallow, suggesting that a treemap could potentially work to visualize
the commit and merge structure of the kernel.

@@

The treemap design is also designed for working with data of differing types. In the
filesystem, there are many kinds of files. There are text files, scripts, images,
binary files, and other types. These can be given colours making differences stand
out. There is no obvious way to assign meaningful types to the commits such that all
the commits within a given merge do not all have the same colour, although a user
could be given a controller to colour by author or number of files edited.

@@

The goal is to build a tool that makes navigation of the kernel commit information
simpler, while providing an explanation of the changes occurring at each commit and
merge. We designed the tool with two use-cases in mind, though a user may switch
between the cases as they work.

\textit{Use-case 1: top-to-bottom approach}\label{sec:usecase1}\\
These are users that are maintaining a section of the kernel and would like to pick
a merge and merge it directly into their current repository, which is useful for
reducing the amount of re-implementation work. For them, it is important to have the
ability to aggregate metadata about files and modules being effected by the merge.
It is also important for them to be able to navigate from the root toward the
leaves.

\textit{Use-case 2: bottom-to-top approach}\label{sec:usecase2}\\
These are users that start with a known merge or commit and would like to see what
other changes are being made in commits that are in the same merge. This is useful
to see how changes in a given file will break other changes made in the surrounding
commits in the same merge. This is primarily for maintainers that need to perform
some implementation work in order to correctly merge patches from the future. We
must provide these users a mechanism for navigating from a single commit toward the
root, allowing them to see the bigger picture.

@@

We root the tree with the merge made by Linus. Each merge may contain zero or more
children, which are other merges and commits. If a merge is cherry-picked or rebased
there will be no children as this information is lost when the rebase occurs.
Commits have no children and are always leaf nodes. The commits contains the
metadata for the changes made. This metadata includes the files changed, the lines
added and removed from each file, the author, the date the commit was merged into
the merge that led to being merged into the kernel, and the date the commit was
authored, the diff, and the commit log. Merges contain less metadata, only storing
the author of the merge, the log, the commit date, and the author date. The details
of the model are outlined by German \cite{German2015}.
